Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Main Bib

Of course, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors. Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ?????? 2010 VERSION MAIN BIB ?????. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.

@@

More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities. In 2010, Freytag and Thurik ????? 2010 VERSION MAINBIB ????? have also studied determinants of entrepreneurship in a cross-country setting and pointed at cultural features. Their results showed that "country specific (cultural) variables seem to explain the preference for entrepreneurship" and self-employment. Yet, not so many empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.

Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996] which is key as "individuals who decide to start a new business exhibit more confidence than those who do not"  ??????? Robin M. Hogarth and Natalia Karelaia 2011 Entrepreneurial success and failure MAIN BIB ?????????. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].

@@

Our focus on the education systems stems partly from experience and from Inglehart research ????????? MAIN BIB 2000 ???????? . Indeed, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions. This assumption draws from Boyd and Vozikis's ??????? MAIN BIB ???????? stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen 1975 ?????? MAIN BIB ???????? who illustrate the relation between beliefs and behaviour as follows:

@@

There could even be an incidence of the intention to perform a certain behaviour on the actual performance of that behaviour, which could lead to look into skills, abilities and willpower. It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" ????? Boyd and Vosikis MAIN BIB ????? but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour". Therefore, we will have to control for this entrepreneurial self-efficacy as we research potential effects of positive reinforcement.

Eventually, this goes without saying, we also looked into other studies connecting educational features and entrepreneurship. As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ??????? Boyd and Vosikis MAIN BIB ??????????? . One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in line with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.

????????????????????????????????????????????????????????????????????????????????????????????

The cross-cultural perspective on teaching and learning proposed by Watkins [@Watkins2010] shall help us compare countries.

Cheng and Wong’s study about school effectiveness in East Asia [@Cheng2006] will also help.

Eventually, to put all these into perspective, along with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.

?????????????????????????????????????????????????????????????????????????????????????????????

>>>>

Of course, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors. Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@freytag2010entrepreneurship]. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.

@@

More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities. In 2010, Freytag and Thurik [@freytag2010entrepreneurship] have also studied determinants of entrepreneurship in a cross-country setting and pointed at cultural features. Their results showed that "country specific (cultural) variables seem to explain the preference for entrepreneurship" and self-employment. Yet, not so many empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.

Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996] which is key as "individuals who decide to start a new business exhibit more confidence than those who do not" [@hogarth2012entrepreneurial]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].

@@

Our focus on the education systems stems partly from experience and from Inglehart research [@inglehart2000modernization] . Indeed, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions. This assumption draws from Boyd and Vozikis's [@boyd1994influence] stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen [@fishbein1975belief] who illustrate the relation between beliefs and behaviour as follows:

@@

There could even be an incidence of the intention to perform a certain behaviour on the actual performance of that behaviour, which could lead to look into skills, abilities and willpower. It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" [@boyd1994influence] but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour". Therefore, we will have to control for this entrepreneurial self-efficacy as we research potential effects of positive reinforcement.

Eventually, this goes without saying, we also looked into other studies connecting educational features and entrepreneurship. As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy [@boyd1994influence]. One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in line with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
